---
title: "Machine Learning"
author: "Alexander Kiskin"
date: "27 сент€бр€ 2015 г."
output: html_document
---

##Loading Data

The training data for this project are available here: [https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv]

The test data are available here: [https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv]

```{r warning=FALSE}
library(caret)
library(randomForest)

trainingset <- read.csv("pml-training.csv", na.strings=c("NA","#DIV/0!", ""))
testingset <- read.csv("pml-testing.csv", na.strings=c("NA","#DIV/0!", ""))
```


##Cleaning Data
To use prediction algorithms we need to exclude all missing values (to be exact - columns with missing values). Additinally we would not use some first columns as predictors, as it makes no sense (like row number, dates, etc.)

```{r}
# Delete columns with all missing values

drops <- c("X", "user_name", "raw_timestamp_part_1", "raw_timestamp_part_2", "cvtd_timestamp", "new_window", "num_window")
trainingset<-trainingset[,!(names(trainingset) %in% drops)]
testingset<-testingset[,!(names(testingset) %in% drops)]

nacheck = colSums(is.na(trainingset))
trainingset<-trainingset[,nacheck == 0]
testingset<-testingset[,nacheck == 0]
```

##Preparing model
Splitting training set in 75%-25% chunks.

```{r}
subsamples <- createDataPartition(y=trainingset$classe, p=0.75, list=FALSE)
subTraining <- trainingset[subsamples, ] 
subTesting <- trainingset[-subsamples, ]
```

We try to use Random forest on 75% chunk as it is known to be one of the most promising at the time. Then we build prediction matrix to chech accuracy using 25% chunk.

```{r}
modelRF <- randomForest(classe ~ . , data=subTraining)

predictionRF <- predict(modelRF, subTesting)

confusionMatrix(predictionRF, subTesting$classe)
```

Accuracy for Random Forest model was 0.994. The expected out-of-sample error is estimated at 0.006, or 0.6%.

##Predicting
Now we will predict results for testingset and write them down into files.

```{r}
predicted <- predict(modelRF, testingset)
predicted

pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0("problem_id_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}
pml_write_files(as.vector(predicted))

```
